Offline Mode for Corporate Mobile Client Security Architecture

### 2016-10-23 docs/papers/2016JGC/2016JGC.tex
several updates

\author{Tatiana Galibus				\and
        Thiago P. B. Vieira			\and
        	Edison P. de Freitas			\and
        	Robson O. Albuquerque		\and
        	João Paulo C. L da Costa		\and
        	Rafael T. de Souza Júnior	\and
        	V. Krasnoproshin1			\and
        	Anton Zaleski				\and
        	H.E.R.M. Vissia				\and
        	Giovanni del Galdo
}

\institute{Tatiana Galibus \at
              Belarusian State University, Minsk, 4, Nezavisimosti, 220030, Belarus
           \and
           Tatiana Galibus \and Thiago P. B. Vieira \and Robson O. Albuquerque \and João Paulo C. L da Costa \and Rafael T. de Souza Júnior  \at
              University of Brasilia, UnB, FT, ENE, CP: 4386, 70910-900, Brasília, Brazil
           \and
           Edison P. de Freitas \at
				Federal University of Rio Grande do Sul, UFRGS, INF, CP: 15064, 91501-970, Porto Alegre, Brazil
           \and
           João Paulo C. L da Costa \and Anton Zaleski \and H.E.R.M. Vissia \and 	Giovanni del Galdo \at
				Institute for Information Technology, Ilmenau University of Technology, Ilmenau, Germany
           \and
           João Paulo C. L da Costa \and Giovanni del Galdo \at
				Fraunhofer Institute for Integrated Circuits IIS, Erlangen, Germany \\
           \and
           ???? \at
				Byelex Multimedia Products BV Argon 1, 4751 XC Oud Gastel, The Netherlands
}

@@

\keywords{ offline mobile cloud security \and offline ABE \and Model Order Selection (MOS) \and user behavior analysis \and secret sharing}

@@

A common practice to provide a cloud solution with stable security is to use a specific type of cloud service, such as Cloud Access Security Broker (CASB) or Cloud Access Control (CAC). These services are specifically designed to bring security at a single access point and provide the coordination of the most important security measures. It is estimated by Gartner \cite{skyhigh2015} that such systems will be used by 85\%  of companies by 2020. Obviously, the reason for this is that the organization of security measures at a single control point allows to control and to monitor the level of cloud protection much more effectively. The basic features of the CASB are: discovery of cloud services, encryption along with tokenization for better search properties, access control, Data Loss Prevention (DLP) services, authentication, and auditing and alerting services \cite{lawson2015}. The protection of the confidential data, according to the standards of CASB deployment should be provided elsewhere, i.e. in transit and at the end-user, i.e. end-client, side \cite{campbell2015}.

@@

Suppose that a SME uses CASB in order to protect data at rest, i.e. while stored on the server-side, in transit, communicating with server, and, in use, while the mobile client is connected to the network. In this case, when the mobile client goes offline with the sensitive corporate data on board all powerful cloud-based tools cannot help and the mobile client has to secure itself with its own limited resources. Moreover, due to the resources constraint, there is a crucial difference in strategy of online and offline mode protection. For example, offline mode does not allow performing the extensive computation and encryption on the mobile device.
Observing the above described landscape, this paper outlines the concept of the offline mobile cloud security.

This paper proposes a novel approach based on powerful cryptographic preventive methods, such as secret sharing (SSS) \cite{galibus2007} and ABE encryption \cite{goyal2006attribute} for securing mobile clients. Moreover, our proposed approach includes the user behavior analysis based on Model Order Selection (MOS) \cite{tenorio2013greatest}, in order to detect possible threats, and to reduce the risks and the harm of the most common threats, which are the expired user misusing password and the intruder attack. The key expiration period is safely incorporated into the proposed system solution in order to enhance security. Additionally, the behavioral analysis can indicate well known malicious behaviors, their variations, as well as novel attacks, which present low or high variance in comparison to legitimate user behaviors. The main target of our proposed solution is to provide a maximum defense at the minimal resource cost.

The paper is structured as follows. Section \ref{sec_related_works} analyzes the most common security problems in the mobile cloud environment and the solutions related to the offline protection in the BYOD world. Section \ref{sec_the_client_security_architecture} outlines the mobile security architecture of the proposed solution. Section \ref{sec_offline_mode} presents the detailed scheme of the proposed solution to the problem of offline mobile client security. Section \ref{sec_algorithms} explains the algorithms for the core security methods: AES, ABE, SSS and MOS. Section \ref{sec_results} discusses the security proofs including the outline of adversary model, the common threat scenarios, the data modeling, the complexity analysis and dicussion of the practical implementation results. Section \ref{sec_conclusion} concludes the paper.

@@

These operations function based on the mobile client architecture, which is depicted in Figure \ref{fig:2}. This architecture consists of the modules of cryptographic functions, threat intelligence infrastructure, communication with server and storage.

\begin{figure}[h!]
	\centering
	\includegraphics[width=8.8cm]{figures/mobileclientarchitecture.eps}
	\caption{The Mobile Client Architecture}
	\label{fig:2}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8.6cm]{figures/offlinesecurityarchitecture.eps}
	\caption{Proposed Architecture for Offline Mobile Security }
	\label{fig:5}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8.6cm]{figures/offlinemodeoperations.eps}
	\caption{Offline Mode Operations}
	\label{fig:6}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8.6cm]{figures/offlineauthorizationworkflow.eps}
	\caption{Offline mode authorization workflow}
	\label{fig:7}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8.6cm]{figures/mosworkflow.eps}
	\caption{The Threat Intelligence Manager Workflow}
	\label{fig:8}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8.6cm]{figures/encryptionworkflow.eps}
	\caption{Encryption workflow}
	\label{fig:9}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8.6cm]{figures/encryptionkeyhierarchy.eps}
	\caption{Encryption key hierarchy}
	\label{fig:10}
\end{figure}

@@

The symmetric encryption on a server side is performed in two steps. First there is a single AES key for preserving the server storage. Second, when the encrypted file is sent from the server to the mobile client another unique AES key is generated, which serves for the encryption on the client side. In other words, along with the encrypted file the user gets his own unique AES key for decrypting the files received. This key is protected by attribute-based public key encryption (ABE).

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8.6cm]{figures/server-sideencryption.eps}
	\caption{Server-side encryption}
	\label{fig:11}
\end{figure}

@@

\subsection{MOS for Threat Intelligence}
\label{sec_mos}
In the context of anomaly-based schemes for attack detection, the proposed behavioral analysis approach applies signal processing techniques, such as Principal Component Analysis and Model Order Selection schemes \cite{tenorio2013greatest}, for automatic identification of attacks or malicious behaviors.

@@

%These features provide the necessary information to apply MOS schemes for evaluating malicious behaviors according to the following scenarios and steps:
%
%\begin{enumerate}
%	\item The hacker accesses the mobile client during a valid session and read/write few files at several folders:
%	\begin{enumerate}
%		\item The hacker steals the device;
%		\item The hacker changes the device to offline mode;
%		\item The hacker accesses the mobile client;
%		\item The current session is valid;
%		\item The hacker read/writes few files at several folders;
%		\item MOS based on correlation analysis is applied to the matrix of number of file operations, grouped by the file system location over time;
%		\item MOS indicates the number of time frames with anomalous behavior;
%	\end{enumerate}
%	\item The hacker accesses the mobile client during a valid session and read/write several files at few folders:
%	\begin{enumerate}
%		\item The hacker steals the device;
%		\item The hacker changes the device to offline mode;
%		\item The hacker accesses the mobile client;
%		\item The current session is valid;
%		\item The hacker read/writes several files at few folders
%		\item MOS based on covariance analysis is applied to the matrix of number of file operations, grouped by the file system location over time
%		\item MOS indicates the number of time frames with anomalous behavior;
%	\end{enumerate}
%	\item The hacker emulates a valid session and read/write few files at several folders: 
%	\begin{enumerate}
%		\item The hacker steals the device;
%		\item The hacker changes the device to offline mode;
%		\item The current session is expired;
%		\item The hacker changes the device time to a valid period for the current session;
%		\item The hacker accesses the mobile client;
%		\item The current session is valid;
%		\item The hacker perform sparse operations during the valid period;
%		\item MOS based on correlation analysis is applied to the matrix of number of file operations, grouped by the file system location over time;
%		\item MOS indicates the number of time frames with anomalous behavior;
%	\end{enumerate}
%	\item The hacker emulates a valid session and read/write several files at few folders: 
%	\begin{enumerate}
%		\item The hacker steals the device;
%		\item The hacker changes the device to offline mode;
%		\item The current session is expired;
%		\item The hacker changes the device time to a valid period for the current session;
%		\item The hacker accesses the mobile client;
%		\item The current session is valid;
%		\item The hacker perform bulk operations during the valid session;
%		\item MOS based on covariance analysis is applied to the matrix of number of file operations, grouped by the file system location over time;
%		\item MOS indicates the number of time frames with anomalous behavior;
%	\end{enumerate}
%\end{enumerate}

@@

		\begin{tabular}[x]{@{}l@{}}Samsung SM-T320 Galaxy\\Tab Pro 8.4\end{tabular}	& 10 mb	& 1041 ms	& 4230 ms	& 298 ms		& 5271 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Samsung SM-T320 Galaxy\\Tab Pro 8.4\end{tabular}	& 1 mb	& 811 ms		& 319 ms		& 23 ms		& 1130 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Samsung SM-T320 Galaxy\\Tab Pro 8.4\end{tabular}	& 1 kb	& 1078 ms	& 1 ms		& 0 ms		& 1080 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Samsung GT-I9190 Galaxy\\S4 Mini\end{tabular}		& 1 b	& 1167ms		& 2 ms		& 0 ms		& 1169 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Samsung GT-I9190 Galaxy\\S4 Mini\end{tabular}		& 1 kb	& 1141ms		& 2 ms		& 0 ms		& 1144 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Samsung GT-I9190 Galaxy\\S4 Mini\end{tabular}		& 1 mb	& 1138 ms	& 368 ms		& 35 ms		& 1506 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Samsung GT-I9190 Galaxy\\S4 Mini\end{tabular}		& 10 mb	& 1131 ms	& 3618 ms	& 324 ms		& 4750 ms	\\ \hline
	\end{tabular}
\end{table*}

@@

The proposed concept of mobile client security has been implemented in the Storgrid protected cloud environment \cite{storgrid2016}. Therefore, the approach is correlated with the practical usability requirements: the corporate user continues to use the mobile storage app in offline and does not need to reload the files every time the key is renewed. This methodology can be used in other mobile clients. The common advantage is that the mobile client performs the operations both in the offline and online mode and uses the key expiry and ABE to protect the privacy of the corporate data. The Table \ref{tab:01} presents the results of mobile client security workflow testing.

Table \ref{tab:01} demonstrates that the mobile client decrypts the data with the acceptable speed. One can compare the speed of ABE/AES decryption (keys and actual data) and the speed of the whole decryption process.

\begin{table*}[!t]
	\caption{Speed of receiving the list of files}
	\label{tab:02}
	\centering
	\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
		\hline \rowcolor{Gray} \begin{tabular}[x]{@{}l@{}}Files\\quantity\end{tabular}	 	& Samples 	& \begin{tabular}[x]{@{}l@{}}Average\\(ms)\end{tabular}	 	& Min (ms) 	& Max (ms) 	& Std. Dev. 	& Error (\%)		& Throughput 	& KB/sec 	& Avg. Bytes \\ \hline
		1		& 1000	& 131	& 29		& 321	& 31.56		& 0.00\%		& 74		& 161.32		& 2233	\\ \hline		
		10		& 1000	& 154	& 37		& 269	& 32.24		& 0.00\%		& 63.4	& 659.79		& 10656	\\ \hline
		100		& 1000	& 396	& 68	 	& 1055	& 87.56		& 0.00\%		& 25		& 2323.2		& 95308	\\ \hline
		1000		& 1000	& 2879	& 475	& 4634	& 496.02		& 0.00\%		& 3.4	& 3178		& 946311	\\ \hline
	\end{tabular}
\end{table*}

\begin{table*}
	\caption{Speed of generating the user keys}
	\label{tab:03}
	\centering
	\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
		\hline \rowcolor{Gray} Label	& Samples	& \begin{tabular}[x]{@{}l@{}}Average\\(ms)\end{tabular}	& Min (ms)	& Max (ms)	& Std. Dev.	& Throughput		& KB/sec		& Avg. Bytes \\ \hline
		\begin{tabular}[x]{@{}l@{}}Login 5\\shares\\available\end{tabular}		& 1000	& 982	& 225	& 1990	& 271.88		& 20.1	& 146.36		& 7459	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Login 10\\shares\\available\end{tabular}	& 1000	& 1140	& 340	& 4176	& 459.3		& 17.3	& 223.88		& 13218	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Login 25\\shares\\available\end{tabular}	& 1000	& 1267	& 887	& 2303	& 192.75		& 15.5	& 294.55		& 19466 \\ \hline
	\end{tabular}
\end{table*}

Table \ref{tab:02} demonstrates the results of testing the speed of the mobile client for receiving and displaying the list of files. The mobile client was tested for displaying up to 1000 files. Around 100 requests were generated from 10 threads.

The mobile client receives and displays the list of files depending on the user attributes with acceptable average speed and the proposed protection scheme is usable. Table \ref{tab:03} demonstrates the results of performance testing of the keys generation procedure on server:

It is easy to observe that the performance does not decrease drastically with the increase of particular user shares. Each key sample generated contains the domain member code, key data and the sharing key value for each file sharing code. It is possible to conclude that the proposed client is not overloaded with calculations due to the carefully selected mathematical operations. It can be successfully used and provides acceptable level of security.

The log analysis of the Log Analysis Center (LAC) has been implemented and evaluated for offline anomaly detection in mobile clients, making it possible to apply anomaly detection techniques in a lightweight fashion, considering low processing requirements for deal with the resource constraints of mobile clients. The evaluation considered the required processing time for anomaly detection from log analysis, measuring the data modeling time through the UAL, the eigenvalue decomposition time and the required time for the EDC MOS scheme execution, which is the scheme that requires less processing capacity and provides more anomaly identification accuracy \cite{da2009comparison,tenorio2013greatest}. The experiments were performed in two mobile devices, Galaxy GT-I9300 and Galaxy Tab SM-T800, with variations of log size and window size. The Galaxy GT-I9300 has Quad-core 1.4 GHz Cortex-A9 processor and 1 GB RAM, while the Galaxy Tab SM-T800 has its processing capacity composed by Quad-core 1.9 GHz Cortex-A15 and quad-core 1.3 GHz Cortex-A7, and 3 GB RAM.

@@

The results show that the lower window size leads to the larger eigenvalue decomposition time, but the largest eigenvalue decomposition time, which was the maximum of 421 milliseconds with average of 347.42 milliseconds. This result highlights an acceptable speed even for the worst evaluated scenario, which is the Galaxy GT-I9300 processing 6MB with window size of 10 minutes.

@@

\section{Conclusion and future work}
\label{sec_conclusion}
An important security issue faced by corporations that use cloud-based systems is how to provide security mechanisms to support offline corporate mobile clients. Once a mobile client releases the connection with the corporate cloud, no security measure implemented in the cloud infrastructure assures the protection of sensitive data stored in the mobile device. Aware of this problem and its importance, this work presented a proposal to address the offline mobile security problem combining a different cryptographic methods. Moreover, this proposed approach also prevents malicious user behavior by applying a MOS-based analytic method.

@@

\begin{acknowledgements}
The authors thank the Brazilian research and innovation agencies FAPDF (Research Support Foundation of the Federal District), FINEP (Agreement RENASIC / PROTO 01.12.0555.00), CAPES and CNPq under the FORTE Project - CAPES Forensic Sciences Announcement 25/2014, under the productivity grant number 303905 / 2014-0, under the PVE project number 88881.030392 / 2013-01 for their financial support on this research, and under the project number 207644/2015-2 for the PDE scholarship in the context of the program CSF- Aerospace Technology.\end{acknowledgements}

>>>>

\author{Tatiana Galibus				\and
        Thiago P. de B. Vieira		\and
        	Edison P. de Freitas			\and
        	Robson O. Albuquerque		\and
        	João Paulo C. L da Costa		\and
        	Rafael T. de Souza Júnior	\and
        Viktor Krasnoproshin			\and
        	Anton Zaleski				\and
        	H.E.R.M. Vissia				\and
        	Giovanni del Galdo
}

\institute{Tatiana Galibus \and Viktor Krasnoproshin \at
              Belarusian State University, Minsk, 4, Nezavisimosti, 220030, Belarus
           \and
           Tatiana Galibus \and Thiago P. B. Vieira \and Robson O. Albuquerque \and João Paulo C. L da Costa \and Rafael T. de Souza Júnior  \at
              University of Brasilia, UnB, FT, ENE, CP: 4386, 70910-900, Brasília, Brazil
           \and
           Edison P. de Freitas \at
				Federal University of Rio Grande do Sul, UFRGS, INF, CP: 15064, 91501-970, Porto Alegre, Brazil
           \and
           João Paulo C. L da Costa \and Giovanni del Galdo \at
				Institute for Information Technology, Ilmenau University of Technology, Ilmenau, Germany
           \and
           João Paulo C. L da Costa \and Giovanni del Galdo \at
				Fraunhofer Institute for Integrated Circuits IIS, Erlangen, Germany
           \and
           Anton Zaleski \and H.E.R.M. Vissia \at
				Byelex Multimedia Products BV Argon 1, 4751 XC Oud Gastel, The Netherlands
}

@@

\keywords{ offline mobile cloud security \and offline attribute-based encryption \and model order selection \and user behavior analysis \and secret sharing}

@@

A common practice to provide a cloud solution with stable security is to use a specific type of cloud service, such as Cloud Access Security Broker (CASB) or Cloud Access Control (CAC). These services are specifically designed to bring security at a single access point and provide the coordination of the most important security measures. Gartner \cite{skyhigh2015} estimates that such systems will be used by 85 \%  of companies by 2020. The reason for this is that the organization of security measures at a single control point allows to control and to monitor the level of cloud protection much more effectively. The basic features of the CASB are: discovery of cloud services, encryption along with tokenization for better search properties, access control, Data Loss Prevention (DLP) services, authentication, and auditing and alerting services \cite{lawson2015}. The protection of the confidential data, according to the standards of CASB deployment should be provided elsewhere, i.e. in transit and at the end-user, i.e. end-client, side \cite{campbell2015}.

@@

Suppose that a SME uses CASB to protect data at rest, i.e. while stored on the server-side, in transit, communicating with server, and, in use, while the mobile client is connected to the network. In this case, when the mobile client goes offline with the sensitive corporate data on board all powerful cloud-based tools cannot help and the mobile client has to secure itself with its own limited resources. Moreover, due to the resources constraint, there is a crucial difference in strategy of online and offline mode protection. For example, offline mode does not allow performing the extensive computation and encryption on the mobile device.
Observing the above described landscape, this paper outlines the concept of the offline mobile cloud security.

This paper proposes a novel approach based on powerful cryptographic preventive methods, such as secret sharing (SSS) \cite{galibus2007} and Attribute-based Encryption (ABE) \citep{goyal2006attribute} for securing mobile clients. Moreover, our proposed approach includes the user behavior analysis based on Model Order Selection (MOS) \cite{tenorio2013greatest}, in order to detect possible threats, and to reduce the risks and the harm of the most common threats, which are the expired user misusing password and the intruder attack. The key expiration period is safely incorporated into the proposed system solution in order to enhance security. Additionally, the behavioral analysis can indicate well known malicious behaviors, their variations, as well as novel attacks, which present low or high variance in comparison to legitimate user behaviors. The main target of our proposed solution is to provide a maximum defense at the minimal resource cost.

The paper is structured as follows. Section \ref{sec_related_works} analyzes the most common security problems in the mobile cloud environment and the solutions for offline protection in the BYOD world. Section \ref{sec_the_client_security_architecture} outlines the mobile security architecture of the proposed solution. Section \ref{sec_offline_mode} presents the detailed scheme of the proposed solution to the problem of offline mobile client security. Section \ref{sec_algorithms} explains the algorithms for the core security methods: AES, ABE, SSS and MOS. Section \ref{sec_results} discusses the security proofs including the outline of adversary model, the common threat scenarios, the data modeling, the complexity analysis and dicussion of the practical implementation results. Section \ref{sec_conclusion} concludes the paper.

@@

These operations function based on the mobile client architecture, which is depicted in Figure \ref{fig:2}.

\begin{figure}[h!]
	\centering
	\includegraphics[width=8cm]{figures/mobileclientarchitecture.eps}
	\caption{The Mobile Client Architecture}
	\label{fig:2}
\end{figure}

This architecture consists of the modules of cryptographic functions, threat intelligence infrastructure, communication with server and storage.

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8cm]{figures/offlinesecurityarchitecture.eps}
	\caption{Proposed Architecture for Offline Mobile Security }
	\label{fig:5}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8cm]{figures/offlinemodeoperations.eps}
	\caption{Offline Mode Operations}
	\label{fig:6}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8cm]{figures/offlineauthorizationworkflow.eps}
	\caption{Offline mode authorization workflow}
	\label{fig:7}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8cm]{figures/mosworkflow.eps}
	\caption{The Threat Intelligence Manager Workflow}
	\label{fig:8}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8cm]{figures/encryptionworkflow.eps}
	\caption{Encryption workflow}
	\label{fig:9}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8cm]{figures/encryptionkeyhierarchy.eps}
	\caption{Encryption key hierarchy}
	\label{fig:10}
\end{figure}

@@

The symmetric encryption on a server side is performed in two steps. First there is a single AES key for preserving the server storage. Second, when the encrypted file is sent from the server to the mobile client another unique AES key is generated, which serves for the encryption on client side. In other words, along with the encrypted file the user gets his own unique AES key for decrypting the files received. This key is protected by attribute-based public key encryption (ABE).

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8cm]{figures/server-sideencryption.eps}
	\caption{Server-side encryption}
	\label{fig:11}
\end{figure}

@@

\subsection{MOS for Threat Intelligence}
\label{sec_mos}
In the context of anomaly-based schemes for attack detection, the proposed behavioral analysis approach applies signal processing techniques, such as Principal Component Analysis and Model Order Selection schemes \cite{tenorio2013greatest}, for automatic detection of attacks or malicious behaviors.

@@

@@

		\begin{tabular}[x]{@{}l@{}}SM-T320 Galaxy Tab Pro 8.4\end{tabular}	& 10 mb	& 1041 ms	& 4230 ms	& 298 ms		& 5271 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}SM-T320 Galaxy Tab Pro 8.4\end{tabular}	& 1 mb	& 811 ms		& 319 ms		& 23 ms		& 1130 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}SM-T320 Galaxy Tab Pro 8.4\end{tabular}	& 1 kb	& 1078 ms	& 1 ms		& 0 ms		& 1080 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}GT-I9190 Galaxy S4 Mini\end{tabular}		& 1 b	& 1167ms		& 2 ms		& 0 ms		& 1169 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}GT-I9190 Galaxy S4 Mini\end{tabular}		& 1 kb	& 1141ms		& 2 ms		& 0 ms		& 1144 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}GT-I9190 Galaxy S4 Mini\end{tabular}		& 1 mb	& 1138 ms	& 368 ms		& 35 ms		& 1506 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}GT-I9190 Galaxy S4 Mini\end{tabular}		& 10 mb	& 1131 ms	& 3618 ms	& 324 ms		& 4750 ms	\\ \hline
	\end{tabular}
\end{table*}

\begin{table*}
	\caption{Speed of receiving the list of files}
	\label{tab:02}
	\centering
	\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
		\hline \rowcolor{Gray} \begin{tabular}[x]{@{}l@{}}Files\\quantity\end{tabular}	 	& Samples 	& \begin{tabular}[x]{@{}l@{}}Average\\(ms)\end{tabular}	 	& \begin{tabular}[x]{@{}l@{}}Min\\(ms)\end{tabular}	& \begin{tabular}[x]{@{}l@{}}Max\\(ms)\end{tabular} 	& Std. Dev. 	& Error (\%)		& Throughput 	& KB/sec 	& Avg. Bytes \\ \hline
		1		& 1000	& 131	& 29		& 321	& 31.56		& 0.00\%		& 74		& 161.32		& 2233	\\ \hline		
		10		& 1000	& 154	& 37		& 269	& 32.24		& 0.00\%		& 63.4	& 659.79		& 10656	\\ \hline
		100		& 1000	& 396	& 68	 	& 1055	& 87.56		& 0.00\%		& 25		& 2323.2		& 95308	\\ \hline
		1000		& 1000	& 2879	& 475	& 4634	& 496.02		& 0.00\%		& 3.4	& 3178		& 946311	\\ \hline
	\end{tabular}
\end{table*}

\begin{table*}
	\caption{Speed of generating the user keys}
	\label{tab:03}
	\centering
	\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
		\hline \rowcolor{Gray} Label	& Samples	& \begin{tabular}[x]{@{}l@{}}Average\\(ms)\end{tabular}	& \begin{tabular}[x]{@{}l@{}}Min\\(ms)\end{tabular}	& \begin{tabular}[x]{@{}l@{}}Max\\(ms)\end{tabular}	& Std. Dev.	& Throughput		& KB/sec		& Avg. Bytes \\ \hline
		\begin{tabular}[x]{@{}l@{}}Login 5 shares available\end{tabular}		& 1000	& 982	& 225	& 1990	& 271.88		& 20.1	& 146.36		& 7459	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Login 10 shares available\end{tabular}	& 1000	& 1140	& 340	& 4176	& 459.3		& 17.3	& 223.88		& 13218	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Login 25 shares available\end{tabular}	& 1000	& 1267	& 887	& 2303	& 192.75		& 15.5	& 294.55		& 19466 \\ \hline
	\end{tabular}
\end{table*}

@@

The proposed concept of mobile client security has been implemented in the Storgrid protected cloud environment \cite{storgrid2016}. Therefore, the approach is correlated with the practical usability requirements: the corporate user continues to use the mobile storage app in offline and does not need to reload the files every time the key is renewed. This methodology can be used in other mobile clients. The common advantage is that the mobile client performs the operations both in the offline and online mode and uses the key expiry and ABE to protect the privacy of the corporate data.

Table \ref{tab:01} presents the results of mobile client security workflow testing and demonstrates that the proposed scheme decrypts the data with acceptable speed. One can compare the speed of ABE/AES decryption (keys and actual data) and the speed of the whole decryption process.

Table \ref{tab:02} demonstrates the results of testing the speed of the mobile client for receiving and displaying the list of files. The client was tested for displaying up to 1000 files. Around 100 requests were generated from 10 threads. It is possible to observe that the client receives and displays the list of files depending on the user attributes with acceptable average speed, showing that the proposed protection scheme is usable.

Table \ref{tab:03} demonstrates the results of performance testing of the keys generation procedure on server. It is possible to observe that the performance does not decrease drastically with the increase of particular user shares. Each key sample generated contains the domain member code, key data and the sharing key value for each file sharing code. It is possible to conclude that the proposed client is not overloaded with calculations due to the carefully selected mathematical operations. It can be successfully used and provides acceptable level of security.

The log analysis of the Log Analysis Center (LAC) has been implemented and evaluated for offline anomaly detection in mobile clients, making it possible to apply anomaly detection techniques in a lightweight fashion, considering low processing requirements for deal with the resource constraints of mobile clients. The evaluation considered the required processing time for anomaly detection from log analysis, measuring the data modeling time through the UAL, the eigenvalue decomposition time and the required time for the EDC MOS scheme execution, which is the scheme that requires less processing capacity and provides more anomaly identification accuracy \cite{da2009comparison,tenorio2013greatest}.

The experiments were performed in two mobile devices, Galaxy GT-I9300 and Galaxy Tab SM-T800, with variations of log size and window size. The Galaxy GT-I9300 has Quad-core 1.4 GHz Cortex-A9 processor and 1 GB RAM, while the Galaxy Tab SM-T800 has its processing capacity composed by Quad-core 1.9 GHz Cortex-A15 and quad-core 1.3 GHz Cortex-A7, and 3 GB RAM.

@@

The results show that the lower window size leads to the larger eigenvalue decomposition time, but the largest eigenvalue decomposition time, which was the maximum of 421 milliseconds with average of 347.42 milliseconds. This result highlights an acceptable speed even for the worst evaluated scenario, which is the case using a Galaxy GT-I9300 for processing 6MB with window size of 10 minutes.

\begin{table*}[!t]
	\caption{EDC MOS scheme processing time for anomaly detection}
	\label{tab:05}
	\centering
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
		\hline \rowcolor{Gray} Device	& \begin{tabular}[x]{@{}l@{}}Log Size\\(MB)\end{tabular}	& \begin{tabular}[x]{@{}l@{}}Window\\(min)\end{tabular}	& \begin{tabular}[x]{@{}l@{}}Avg. EDC.\\(ms)\end{tabular}	& \begin{tabular}[x]{@{}l@{}}Std. EDC.\\(ms)\end{tabular}	& \begin{tabular}[x]{@{}l@{}}Min. EDC.\\(ms)\end{tabular}	& \begin{tabular}[x]{@{}l@{}}Max. EDC.\\(ms)\end{tabular}	\\ \hline
		Galaxy GT-I9300	& 6	& 60	& 5.27	& 4.04	& 3	& 20	\\ \hline
		Galaxy GT-I9300	& 6	& 40	& 10.78	& 6.37	& 6	& 34	\\ \hline
		Galaxy GT-I9300	& 6	& 20	& 32.62	& 12.44	& 21	& 88	\\ \hline
		Galaxy GT-I9300	& 6	& 10	& 115.08	& 17.45	& 88	& 158	\\ \hline
		Galaxy GT-I9300	& 4.1	& 60	& 5.68	& 4.18	& 3	& 23	\\ \hline
		Galaxy GT-I9300	& 4.1	& 40	& 10.76	& 5.31	& 7	& 27	\\ \hline
		Galaxy GT-I9300	& 4.1	& 20	& 37.58	& 10.30	& 23	& 61	\\ \hline
		Galaxy GT-I9300	& 4.1	& 10	& 125.98	& 18.56	& 101	& 191	\\ \hline
		Galaxy GT-I9300	& 1.4	& 60	& 4.92	& 3.49	& 3	& 17	\\ \hline
		Galaxy GT-I9300	& 1.4	& 40	& 9.00	& 4.23	& 6	& 25	\\ \hline
		Galaxy GT-I9300	& 1.4	& 20	& 30.14	& 9.21	& 19	& 62	\\ \hline
		Galaxy GT-I9300	& 1.4	& 10	& 100.62	& 15.83	& 69	& 163	\\ \hline
		Galaxy Tab SM-T800	& 6	& 60	& 1.84	& 0.65	& 1	& 3	\\ \hline
		Galaxy Tab SM-T800	& 6	& 40	& 3.26	& 1.24	& 2	& 7	\\ \hline
		Galaxy Tab SM-T800	& 6	& 20	& 10.90	& 2.40	& 9	& 21	\\ \hline
		Galaxy Tab SM-T800	& 6	& 10	& 41.86	& 7.33	& 34	& 60	\\ \hline
		Galaxy Tab SM-T800	& 4.1	& 60	& 1.85	& 0.60	& 1	& 3	\\ \hline
		Galaxy Tab SM-T800	& 4.1	& 40	& 3.62	& 1.10	& 2	& 8	\\ \hline
		Galaxy Tab SM-T800	& 4.1	& 20	& 12.04	& 2.79	& 9	& 22	\\ \hline
		Galaxy Tab SM-T800	& 4.1	& 10	& 40.16	& 6.48	& 35	& 60	\\ \hline
		Galaxy Tab SM-T800	& 1.4	& 60	& 1.98	& 0.89	& 1	& 6	\\ \hline
		Galaxy Tab SM-T800	& 1.4	& 40	& 3.30	& 1.16	& 2	& 7	\\ \hline
		Galaxy Tab SM-T800	& 1.4	& 20	& 10.48	& 2.90	& 8	& 21	\\ \hline
		Galaxy Tab SM-T800	& 1.4	& 10	& 34.52	& 4.08	& 30	& 45	\\ \hline
	\end{tabular}
\end{table*}

@@

\section{Conclusion and future work}
\label{sec_conclusion}

An important security issue faced by corporations that use cloud-based systems is how to provide security mechanisms to support offline corporate mobile clients. Once a mobile client releases the connection with the corporate cloud, no security measure implemented in the cloud infrastructure assures the protection of sensitive data stored in the mobile device. Aware of this problem and its importance, this work presented a proposal to address the offline mobile security problem combining a different cryptographic methods. Moreover, this proposed approach also prevents malicious user behavior by applying a MOS-based analytic method.

@@

\begin{acknowledgements}
The authors thank the Brazilian research and innovation agencies FAPDF (Research Support Foundation of the Federal District), FINEP (Agreement RENASIC / PROTO 01.12.0555.00), CAPES and CNPq under the FORTE Project - CAPES Forensic Sciences Announcement 25/2014, under the productivity grant number 303905 / 2014-0, under the PVE project number 88881.030392 / 2013-01 for their financial support on this research, and under the project number 207644/2015-2 for the PDE scholarship in the context of the program CSF - Aerospace Technology.\end{acknowledgements}
